%%%%%%%%%%%%%%%%%
% Credits
% Format and usage inspired by to CV template created using altacv.cls written by LianTze Lim (liantze@gamil.com).
%
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
\documentclass[10pt,a4paper,academicons]{altacv}

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}

% mainfont
\setmainfont{Lato}

% colors 
\definecolor{Light Blue}{HTML}{336699}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{Blue}{HTML}{003366}
\colorlet{heading}{Blue}
\colorlet{accent}{Light Blue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% bullets for skills listed 
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Anshuman Patnaik}
\tagline{New Grad \& Aspiring Software Engineer}
\personalinfo{%
  \email{anshuman.patnaik2008@gmail.com}
  \phone{(519) 574-9852}
  \linkedin{linkedin.com/in/a3patnaik}
  \github{github.com/patnaa2}
}

\begin{adjustwidth}{}{-8cm}
\makecvheader
\end{adjustwidth}

\cvsection[sidebar]{Experience}

\cvevent{Technical Project Manager/Software Engineer Intern}{A9.com - Advertising Technology}{Summer 2017}{Palo Alto, CA}
\begin{itemize}
\item Investigated potential sources of errors in forecasting for an advertising program through data analaysis and talking to relevant stakeholders.
\item Developed a roadmap and established product requirements and design for the above forecasting product.
\item Created an ETL pipeline to aggregate data from multiple sources to report on advertising supply metrics.
\item Built a dashboard using Angular and Spark to surface insights about a new advertising delivery pattern.
\end{itemize}

\divider

\cvevent{Infrastructure Engineer}{Wish (ContextLogic Inc.)}{Winter and Fall
2016 }{San Francisco, CA}
\begin{itemize}
\item Established a framework to allow developers to easily denormalize collections through timed migrations leveraging an experiment framework.
\item Designed and built a framework to execute tools, commands and monitor the entire MongoDB cluster.
\item Created a tool to launch a production-ready sharded MongoDB cluster in 5
    minutes using AWS, Chef and Python.
\item Architected and facilitated a migration of a portion of the existing
    database cluster to AWS, reducing main cluster load by 30\%. 
\item Validated, automated, and executed two major upgrades on the MongoDB
    cluster leveraging benchmarking tools and in-house orchestration tools, in
        conjunction with Chef.
\item Improved the robustness of existing infrastructure monitoring tools through increased parallelization and higher fault tolerance.
\item Developed a log parsing tool for database logs to analyze and detect bad queries ad-hoc.
\end{itemize}

\divider

\cvevent{Database Engineer}{Rubicon Project}{Summer 2015}{Los Angeles, CA}
\begin{itemize}
\item Maintained and optimized production MySQL database clusters through tasks such as query optimization, load balancing, and database backup automation.
\item Designed and built a dashboard using a Ruby-based framework to display critical system health and current task metrics.
\end{itemize}

\cvsection{Projects}

\cvurlevent{WaterBud}{}{}{}{youtube.com/watch?v=esiiBljmMzM}
\begin{itemize}
\item A proposed solution to curb household water waste by providing detailed breakdown of water use in a household.
\item Designed and built a MVP using Raspberry Pi, Tornado, Flask, and Python.
\end{itemize}

\end{document}
